An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2017-03-22 uai2017/paper.tex
Updated figures after fixing logistic regression bug with log u vs log (1)

Figure~\ref{fig:logistic_histograms_mnist8m} shows log-log histograms of
minibatch sizes for the methods on MNIST-100k.
(Figure~\ref{fig:logistic_histograms_mnist} in Appendix~\ref{app:logistic}
contains results for MNIST-13k.) The histograms only represent one
representative trial; Table~\ref{tab:logistic} contains the average of the
average minibatch sizes ($\pm$ one standard deviation) across all trials. {\sc
MHminibatch}, with average minibatch sizes of 133.7 and 242.4 for MNIST-13k and
MNIST-100k, respectively, consumes more than 7x and 4x fewer data points than
the next-best method, {\sc AustereMH(nc)}.  We reiterate, however, that both
{\sc AustereMH(nc)} and {\sc MHSubLhd} require computing $\log p(x_i|\theta)$
and $\log p(x_i|\theta')$ for all $x_i$ each iteration. Our results here do not
count that extra data consumption. Only our method and {\sc AustereMH(c)} rely
solely on the minibatch of data each iteration.

@@

\begin{table}[t]
\caption{Average minibatch sizes ($\pm$ one standard deviation) on logistic
regression on MNIST-13k and MNIST-100k.  The averages are taken over 10
independent trials (5000 samples each) for MNIST-13k and 5 independent trials
(3000 samples each) for MNIST-100k.}
\small % Daniel: yeah, sorry, but otherwise it doesn't fit in a column
\label{tab:logistic}
\vskip 0.15in
\begin{center}
\begin{tabular}{l l l l}
\textbf{Method/Data} & \textbf{MNIST-13k} & \textbf{MNIST-100k}  \\
\hline \\
{\sc MHminibatch}   & $133.7\pm 4.7$    & $242.4 \pm 12.4$ \\
{\sc AustereMH(nc)} & $973.8\pm 49.8$   & $1098.3 \pm 44.9$ \\
{\sc AustereMH(c)}  & $1924.3\pm 52.4$  & $2795.6 \pm 364.0$ \\
{\sc MHSubLhd}      & $10783.4\pm 78.9$ & $14977.3 \pm 582.0$ \\
\end{tabular}
\end{center}
\vskip -0.1in
\end{table}

@@

\begin{figure*}[t]
	\centering
    \includegraphics[width=0.9\linewidth]{logistic_regression_step_size_tests.png}
	\caption{
    \textbf{Daniel: TODO describe}
    }
	\label{fig:logistic_histograms_appendix}
\end{figure*}

>>>>

Figure~\ref{fig:logistic_histograms_mnist8m} shows log-log histograms of
minibatch sizes for the methods on MNIST-100k.
(Figure~\ref{fig:logistic_histograms_mnist} in Appendix~\ref{app:logistic}
contains results for MNIST-13k.) The histograms only represent one
representative trial; Table~\ref{tab:logistic} contains the average of the
average minibatch sizes ($\pm$ one standard deviation) across all trials. {\sc
MHminibatch}, with average minibatch sizes of 125.4 and 216.5 for MNIST-13k and
MNIST-100k, respectively, consumes more than 7x and 4x fewer data points than
the next-best method, {\sc AustereMH(nc)}.  We reiterate, however, that both
{\sc AustereMH(nc)} and {\sc MHSubLhd} require computing $\log p(x_i|\theta)$
and $\log p(x_i|\theta')$ for all $x_i$ each iteration. Our results here do not
count that extra data consumption. Only our method and {\sc AustereMH(c)} rely
solely on the minibatch of data each iteration.

@@

\begin{table}[t]
\caption{Average minibatch sizes ($\pm$ one standard deviation) on logistic
regression on MNIST-13k and MNIST-100k.  The averages are taken over 10
independent trials (5000 samples each) for MNIST-13k and 5 independent trials
(3000 samples each) for MNIST-100k.}
\small % Daniel: yeah, sorry, but otherwise it doesn't fit in a column
\label{tab:logistic}
\vskip 0.15in
\begin{center}
\begin{tabular}{l l l l}
\textbf{Method/Data} & \textbf{MNIST-13k} & \textbf{MNIST-100k}  \\
\hline \\
{\sc MHminibatch}   & $125.4\pm 9.2$    & $216.5 \pm 7.9$ \\
{\sc AustereMH(nc)} & $973.8\pm 49.8$   & $1098.3 \pm 44.9$ \\
{\sc AustereMH(c)}  & $1924.3\pm 52.4$  & $2795.6 \pm 364.0$ \\
{\sc MHSubLhd}      & $10783.4\pm 78.9$ & $14977.3 \pm 582.0$ \\
\end{tabular}
\end{center}
\vskip -0.1in
\end{table}

@@

\begin{figure*}[t]
	\centering
    \includegraphics[width=0.9\linewidth]{logistic_regression_step_size_tests.png}
	\caption{
    Effect of changing the proposal step size $\sigma$ for
    {\sc MHminibatch}.
    }
	\label{fig:logistic_histograms_appendix}
\end{figure*}
